---
title: "wow-dc-text-analysis"
author: "Nick"
date: "9/13/2021"
output: github_document
---

## WoW with WOW discord text mining

This project's main aim is to explore various text mining methods with R, following along Dave Langer's [Text Analytics with R series](https://www.youtube.com/watch?v=4vuw0AsHeGw&list=PLTJTBoU5HOCR5Vkah2Z-AU76ZYsZjGFK6&ab_channel=DataScienceDojo) here.

I will be exploring data from a World of Warcraft Q&A discord channel.

Have fun learning along with me!

## Required packages

```{r packages-list, message = FALSE}
library(tidyverse)
library(jsonlite)
library(lubridate)
```

## Getting the data

To get the discord data required for analysis, I used Tyrrrz's [DiscordChatExporter](https://github.com/Tyrrrz/DiscordChatExporter), and pulled the data out from the `ask for help` channel from the r/WoW Discord group. 

Note that automating your Discord account is technically against Discord's TOS, so use with caution, and don't pull out data too quickly which might flag your account.

This channel is almost a Q&A of sorts, which could show trends in what people are excited or need help the most with in World of Warcraft.

Data can be extracted in various output types, but we will be using JSON to get the neatest dataset possible. Now, we'll get the data into R using the `jsonlite` package.

```{r initial-data-import, echo = FALSE}

initial_discord_dump <- fromJSON("C:/Users/herkm/Desktop/R Workspace/wow-discord-text-project/[CHAT EXPORT] World of Warcraft - Serious Channels - ask-for-help [205710841146900480].json")

str(initial_discord_dump)
```
Getting a list of lists, we find that we are only interested in one section of the data - the `messages` list, and its content. Let's extract that and turn it into a dataframe

```{r data-framed-initial-import}
discord_messages_only <- tibble(initial_discord_dump$messages)

```
Now, we have to filter further, removing unnecessary columns like attachments, isPinned, etc. Also, we want to unnest the author dataframe, and remove columns that are unnecessary for analysis, namely the `color`, `avatarUrl`, `nickname`, and `isBot` columns.

```{r dplyr-data-frame-construction}
time_and_content_only <- discord_messages_only %>% 
  select(timestamp, content)

wow_help_authors_only <- discord_messages_only %>% 
  select(author)

wow_help_authors_only_df <- do.call(data.frame, wow_help_authors_only) %>% 
  select(-author.color, -author.avatarUrl, -author.nickname, -author.isBot)

wow_content_filtered <- bind_cols(time_and_content_only, wow_help_authors_only_df)

str(wow_content_filtered)
```
Viola! we now have a great looking data table for text analysis.
